A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-05-19 paper/paper.tex
Mention in walkthrough that we add a pair to the mapping at each level of the search tree
matching -> mapping

The algorithm builds up a mapping $M$, starting with the empty mapping
$\emptyset$. Select a vertex in $\V(\graphG)$ as the first vertex to be mapped; in
our example we will arbitrarily choose vertex $1$. Each of the vertices in
$\V(\graphH)$ to which vertex $1$ may be mapped will be tried in turn, and finally the
possibility where vertex $1$ remains unmatched will be tried.

@@

The algorithm backtracks when the incumbent (the largest matching found so far) is at least as large
as a calculated bound given $M$ and the current labelling. To demonstrate how
this bound is calculated, we consider the situation one level deeper in the
search tree shown in \cref{fig:alg4}.

Three vertex labels are used: 100,
101, and 111.  The first two of these only appear in one graph, and therefore
there is no way to add a pair of vertices with label 100 or 101 to the mapping.
The final label, 111, appears once in $\graphG$ and twice in $\graphH$, and therefore at
most one pair with this label can be added to $M$.  Thus, the upper bound on
matching size is $|M| + 1 = 4$. The general formula for the upper bound is
\begin{multline*}
    \mathit{bound} = |M| + \sum_{l \in L} \min\big(|\{ v \in \V(\graphG) : \vtxlabel(v)=l\}|, \\[-0.3cm]
        |\{ v \in \V(\graphH) : \vtxlabel(v)=l \}|\big) \text{,}
\end{multline*} where $L$ is the set of labels used in both graphs.

@@

The basic \McSplit\ is beaten by the $k{\downarrow}$ algorithm of
\citet{UpcomingAAAIPaper} on this dataset. However, we can modify the \McSplit\
algorithm to use a top-down strategy similar to that used by $k{\downarrow}$  by
calling the main \FuncSty{McSplit} method once per goal size ($g, g-1, g-2,
\dots$); we backtrack (\lineref{PruneSearch} of \cref{McSplitAlg}) when the
bound is strictly less than the goal size, and terminate when a solution of the
goal size is found. We expect that this could do well because in many cases the
matching covers nearly all of the smaller graph---indeed,
\cref{figure:sip-cumulative} shows that this approach is the strongest on these
instances, and \McSplit{$\downarrow$} is the best algorithm for every choice of timeout.

>>>>

The algorithm builds up a mapping $M$, starting with the empty mapping
$\emptyset$ and adding a $(v_i, w_i)$ pair at each level of the search tree.
Select a vertex in $\V(\graphG)$ as the first vertex to be mapped; in our
example we will arbitrarily choose vertex $1$. Each of the vertices in
$\V(\graphH)$ to which vertex $1$ may be mapped will be tried in turn, and
finally the possibility where vertex $1$ remains unmatched will be tried.

@@

The algorithm backtracks when the incumbent (the largest mapping found so far) is at least as large
as a calculated bound given $M$ and the current labelling. To demonstrate how
this bound is calculated, we consider the situation one level deeper in the
search tree shown in \cref{fig:alg4}.

Three vertex labels are used: 100,
101, and 111.  The first two of these only appear in one graph, and therefore
there is no way to add a pair of vertices with label 100 or 101 to the mapping.
The final label, 111, appears once in $\graphG$ and twice in $\graphH$, and therefore at
most one pair with this label can be added to $M$.  Thus, the upper bound on
mapping size is $|M| + 1 = 4$. The general formula for the upper bound is
\begin{multline*}
    \mathit{bound} = |M| + \sum_{l \in L} \min\big(|\{ v \in \V(\graphG) : \vtxlabel(v)=l\}|, \\[-0.3cm]
        |\{ v \in \V(\graphH) : \vtxlabel(v)=l \}|\big) \text{,}
\end{multline*} where $L$ is the set of labels used in both graphs.

@@

The basic \McSplit\ is beaten by the $k{\downarrow}$ algorithm of
\citet{UpcomingAAAIPaper} on this dataset. However, we can modify the \McSplit\
algorithm to use a top-down strategy similar to that used by $k{\downarrow}$  by
calling the main \FuncSty{McSplit} method once per goal size ($g, g-1, g-2,
\dots$); we backtrack (\lineref{PruneSearch} of \cref{McSplitAlg}) when the
bound is strictly less than the goal size, and terminate when a solution of the
goal size is found. We expect that this could do well because in many cases the
maximum common subgraph covers nearly all of the smaller graph---indeed,
\cref{figure:sip-cumulative} shows that this approach is the strongest on these
instances, and \McSplit{$\downarrow$} is the best algorithm for every choice of timeout.
